Parameter-less Population Pyramid

### 2014-03-19 Parameterless Population Pyramid/main.tex
Made paper unanonymous, added clustering psuedocode.

\numberofauthors{2} %
\begin{comment}
\author{
% 1st. author
\alignauthor
Brian W. Goldman\\
       \affaddr{BEACON Center for the Study of Evolution in Action}\\
       \affaddr{Michigan State University, U.S.A.}\\
       \email{brianwgoldman@acm.org}
% 2nd. author
\alignauthor
William F. Punch\\
       \affaddr{BEACON Center for the Study of Evolution in Action}\\
       \affaddr{Michigan State University, U.S.A.}\\
       \email{punch@msu.edu}
}
%\end{comment}
%\begin{comment}
\author{
% 1st. author
\alignauthor
Anonymous\\
       \affaddr{Group}\\
       \affaddr{Organization}\\
       \email{email@site.com}
% 2nd. author
\alignauthor
Anonymous\\
       \affaddr{Group}\\
       \affaddr{Organization}\\
       \email{email@site.com}
}
%\end{comment}

@@

@@

In total, our experiments performed 100 runs of each optimization algorithm across
7 benchmark problems, with each run limited to 100 million evaluations.
In performing data collection, we performed over 150,000 runs, totaling approximately
1.5 trillion evaluations.  Of these, approximately 100,000 runs were used to optimally
set the population size of LTGA.  Note that these runs are considered a training phase,
and therefore all results for LTGA use independent runs to create a testing phase.
This was the only algorithm that received tuning.  As such, LTGA should have a significant
advantage over the others in that it has pre-learned the correct population size.
All of the code used to perform our experiments
as well as individual run results and analysis scripts are available from our
website.\footnote{\url{https://name.of.site.removed/anonymous}}  The results
are summarized in Figure~\ref{fig-results} and Table~\ref{table-results}.

>>>>

\numberofauthors{2} %
%\begin{comment}
\author{
% 1st. author
\alignauthor
Brian W. Goldman\\
       \affaddr{BEACON Center for the Study of Evolution in Action}\\
       \affaddr{Michigan State University, U.S.A.}\\
       \email{brianwgoldman@acm.org}
% 2nd. author
\alignauthor
William F. Punch\\
       \affaddr{BEACON Center for the Study of Evolution in Action}\\
       \affaddr{Michigan State University, U.S.A.}\\
       \email{punch@msu.edu}
}
%\end{comment}
\begin{comment}
\author{
% 1st. author
\alignauthor
Anonymous\\
       \affaddr{Group}\\
       \affaddr{Organization}\\
       \email{email@site.com}
% 2nd. author
\alignauthor
Anonymous\\
       \affaddr{Group}\\
       \affaddr{Organization}\\
       \email{email@site.com}
}
%\end{comment}

@@

\begin{figure}
  \begin{algorithmic}
  \Procedure{Cluster-Creation}{}
    \State $unmerged \leftarrow \{\{i\} | 0 \le i < N\}$
    \State $useful \leftarrow unmerged$
    \While{$|unmerged|>0$}
      \State $C_i, C_j \leftarrow \min_{C_i,C_j \in unmerged} D(C_i, C_j)$
      \State $unmerged \leftarrow unmerged - \{C_i, C_j\} + \{C_i \cup C_j\}$
      \State $useful \leftarrow \{C_i \cup C_j\}$
      \If{$D(C_i, C_j) == 0$}
        \State $useful \leftarrow useful - \{C_i, C_j\}$
      \EndIf
    \EndWhile
    \State Order $useful$ based on cluster size, smallest first.
    \State Remove largest cluster from $useful$.

    \Return $useful$
  \EndProcedure
\end{algorithmic}
  \caption{Algorithm describing how clusters are created using Equation~\ref{eq-distance}.}
  \label{fig:cluster-creation}
\end{figure}

@@

In total, our experiments performed 100 runs of each optimization algorithm across
7 benchmark problems, with each run limited to 100 million evaluations.
In performing data collection, we performed over 150,000 runs, totaling approximately
1.5 trillion evaluations.  Of these, approximately 100,000 runs were used to optimally
set the population size of LTGA.  Note that these runs are considered a training phase,
and therefore all results for LTGA use independent runs to create a testing phase.
This was the only algorithm that received tuning.  As such, LTGA should have a significant
advantage over the others in that it has pre-learned the correct population size.
All of the code used to perform our experiments
as well as individual run results and analysis scripts are available from our
website.\footnote{\url{https://github.com/brianwgoldman/Parameter-less_Population_Pyramid}}  The results
are summarized in Figure~\ref{fig-results} and Table~\ref{table-results}.
